Examining Crowd Work and Gig Work Through The Historical Lens of Piecework

### 2017-05-05 chi/piecework/presentation/introduction.tex
nightly updates

% \frame<1-3>[frame1]{
\begin{frame}<-2>[label=returnable]{A brief glossary}
      \begin{itemize}
        \item<1> \textit{Crowd work}: digitally mediated \textbf{information work}
        (for example, work done on Amazon Mechanical Turk, UpWork, or 99designs)~\cite{crowdworkFuture}
        \item<2> \textit{Gig work}: digitally mediated (but often \textbf{physically embodied}) one--off jobs,
        such as
        \textit{driving},
        \textit{courier services},
        and \textit{administrative support}~\cite{friedman2014workers,Parigi:2016:GE:3026779.3013496}
        \item<3> \textit{Piecework}: Payment for \textit{output} rather than for \textit{time}
      \end{itemize}
\end{frame}

@@

    \vspace{5mm}
    \includegraphics[width=\textwidth]{figures/complexity/hexRepeat.png}
    \vspace{5mm}

>>>>

% \frame<1-3>[frame1]{
\begin{frame}<-2>[label=returnable]{A brief glossary}
      \begin{itemize}
        \item<1-> \textit{Crowd work}: digitally mediated \textbf{information work}
        (for example, work done on Amazon Mechanical Turk, UpWork, or 99designs)~\cite{crowdworkFuture}
        \item<2-> \textit{Gig work}: digitally mediated (but often \textbf{physically embodied}) one--off jobs,
        such as
        \textit{driving},
        \textit{courier services},
        and \textit{administrative support}~\cite{friedman2014workers,Parigi:2016:GE:3026779.3013496}
        \item<3-> \textit{Piecework}: Payment for \textit{output} rather than for \textit{time}
      \end{itemize}
\end{frame}

@@

    \vspace{5mm}
    \includegraphics[width=\textwidth]{figures/hexagonflattened.png}
    \vspace{5mm}
